---
title: "Stat 184 Project"
author: "ProjectTeam6-3"
date: "5/3/2021"
output: html_notebook 
---



#### Load Packages
```{r message=FALSE}
library(tidyverse) 
```

#### Read in Data and Convert Stat files to data frames
```{r}
Memfan <- read.csv("Memorial_Fantasy.csv", header = T)
Pgafan <- read.csv("PGA_Fantasy.csv", header = T)
Schfan <- read.csv("Schwab_Fantasy.csv", header = T)

Memstat<- read.delim("Memorial_Stats.txt", header = T )
Memstats <-  as.data.frame(matrix(Memstat$Data, ncol=9, byrow=TRUE))

Pgastat<- read.delim("PGA_Stats.txt", header = T)
Pgastats <-  as.data.frame(matrix(Pgastat$Data, ncol=9, byrow=TRUE))

Schstat<- read.delim("Schwab_Stats.txt", header = T)
Schstats <-  as.data.frame(matrix(Schstat$Data, ncol=9, byrow=TRUE))
```

#### Join Fantasy and Statistics to Create One Data Frame for Each of Three Tournaments

```{r}
Memorial <- Memstats %>%
  inner_join(Memfan, by=c("V2"= "Name"))

Pga <- Pgastats %>%
  inner_join(Pgafan, by=c("V2"= "Name")) 


Schwab <- Schstats %>%
  inner_join(Schfan, by=c("V2"= "Name"))
```

#### Combine the Three Tournament Data Frames to Final Data Frame
Include paragraph explaining what the R statements are "doing" and what you are trying to accomplish with these statements.

```{r}
All <- rbind(Memorial, Pga, Schwab)
names(All)[1:9] <- c('Position', 'Player', 'Score', 
                          'Putt', 'ARG', 'App', 'OTT', 'T2G', 'Total')

All$Score <- fct_recode(All$Score, "0" = "E") 

Top10 <- 
  All %>%
  group_by(Tournament) %>%
  mutate(Score = as.numeric(as.character(factor(Score)))) %>%
  mutate(rank = rank(Score, ties.method = "min")) %>%
  mutate(top10 = if_else(rank <= 10, 'Yes', 'No')) %>%
  mutate(MadeCut = if_else(Position =='CUT', 'No', 'Yes')) %>%
  mutate(SalaryRange = ifelse(grepl("^6", Salary), "6000s",
                       ifelse(grepl("^7", Salary), "7000s",
                       ifelse(grepl("^8", Salary), "8000s",
                       ifelse(grepl("^9" , Salary), "9000s",
                       ifelse(grepl("^10", Salary), "10000s", "11000s"))))))

TournPlayed <- All %>%
  select((Player)) %>%
  group_by(Player) %>%
  mutate(tournplayed = n()) %>%
  distinct()

AvgScore <- All %>%
    select(Player, Score, Tournament) %>%
    mutate(Score = as.numeric(as.character(factor(Score)))) %>%
    spread(Tournament, Score) %>%
    mutate(avg = round(rowMeans(.[2:4], na.rm=TRUE), 1))

Results_Player <- Top10 %>%
  left_join(TournPlayed, by = "Player")

AllResults <- Results_Player %>%
  left_join(AvgScore, by = "Player")
```

#### Is the Score or FPTS (Fantasy Points) more indicative of what players would make the cut?
We formulated this graph to figure out whether the MadeCut category was indicated from trends in the scores or trends in the fantasy points. We found by creating this graph that the point at which fantasy scores fall below around 40 points indicates a cut off for who made the cut off or not. This differs from the scores, where players who made the cut or did not have shown to have overlapping Scores. Our graph displays that fantasy points have a higher correlation to whether a player made the cut over their Score per tournament.
```{r}
AllResults %>%
  ggplot(aes(x = Score,y = FPTS, color = MadeCut))+
  geom_point()+
  facet_wrap(~Tournament)
```
#### How does a player's rank or score affect how much money they make per tournament?
The first graph explores the correlation between ranks and salary, where there seems to be a general negative correlation, meaning that the lower you are ranked, the lower your salary is going to be on average. In addition, we added the made cut category of yes or no as the color to signify where in the data the players are not longer eligible to compete for another tournament. Our second graph also shows how the average score (from all tournaments), correlates to being within a certain salary range. We found that those within the lowest salary range, 6000s, on aberage had the widest distrubtuon of scores with an abundance of them being high, which signifies a bad game in golf. As the salary ranges start getting high though, the mean score begins to decrease, which is telling that the average score correlates to a player's salary range.
```{r}
AllResults %>%
  ggplot(aes(x=rank, y=Salary, color = MadeCut))+
  geom_point()
```
```{r}
AllResults$SalaryRange <- factor(AllResults$SalaryRange, levels = c("6000s", "7000s", "8000s", "9000s", "10000s", "11000s"))

AllResults %>%
  ggplot(aes(x=SalaryRange, y =avg))+
  geom_boxplot(aes(fill=SalaryRange))+
  ylab("Average Score")+
  xlab("Salary Range")+
  theme(axis.text.x = element_text(angle = 30))

```


